---
title: "ST 558 Homework 3"
author: "Lee Bennett"
format: html
editor: visual
---

## Task 1: Control Flow Practice

To get started, we'll add a new column called `status` to each data frame in `bp_list`:

```{r}
load("hw2_list.rda")

bp_list$treatment$status <- character(20)
bp_list$placebo$status <- character(10)

```

Next, we'll classify each post-treatment blood pressure measurement as

-   Normal (≤120 mm Hg)

-   Borderline (\>120 and ≤ 140 mm Hg)

-   High (≥140 mmHg)

using a `for` loop and `if/then/else` logic:

```{r}
for (i in 1:20) 
{
if (bp_list$treatment$post_bp[i] <= 120) bp_list$treatment$status[i] <- "Normal"
else if (bp_list$treatment$post_bp[i]>120 &  bp_list$treatment$post_bp[i]<=140) bp_list$treatment$status[i] <- "Borderline"
else bp_list$treatment$status[i] <- "High"
}
head(bp_list$treatment)
```

A similar `for` loop does the same classification for the placebo group:

```{r}
for (i in 1:10) 
{
if (bp_list$placebo$post_bp[i] <= 120) bp_list$placebo$status[i] <- "Normal"
else if (bp_list$placebo$post_bp[i]>120 &  bp_list$placebo$post_bp[i]<=140) bp_list$placebo$status[i] <- "Borderline"
else bp_list$placebo$status[i] <- "High"
}
head(bp_list$placebo)
```

## Task 2: Function Writing

For this task, we create a function that takes a list containing 2 data frames (`treatment` and `placebo`) and a summary function (with a default value of `mean`) as arguments:

```{r}
df_stat <- function(df_list,stat="mean") {
  my_fun <- get(stat)
  trt_sum<-c(my_fun(df_list$treatment$pre_bp),my_fun(df_list$treatment$post_bp),my_fun(df_list$treatment$diff_bp))
  placebo_sum<-c(my_fun(df_list$placebo$pre_bp),my_fun(df_list$placebo$post_bp),my_fun(df_list$placebo$diff_bp))
  final_sum<-c(trt_sum,placebo_sum)
  
  vec_names<-c("Pre-treatment","Post-treatment","Treatment difference","Pre-placebo","Post-placebo","Placebo difference")
  result_names<-paste(vec_names,stat)
  
  names(final_sum)<-result_names
  return(final_sum)
}
```

We can now apply this function to the `bp_list` object to obtain a variety of summary statistics for the blood pressure data:

1.  Mean:

```{r}
df_stat(bp_list)
```

2.  Variance:

```{r}
df_stat(bp_list,stat="var")
```

3.  Standard deviation:

```{r}
df_stat(bp_list,stat="sd")
```

4.  Minimum:

```{r}
df_stat(bp_list,stat="min")
```

5.  Maximum:

```{r}
df_stat(bp_list,stat="max")
```
